\sysfull

### 2018-08-05 paper/asplos19/evaluation.tex
minor modification

In a separate experiment, we have enabled task downsizing in \sys and measured
the execution time for \textit{fft} benchmark at 60\,cm from the signal
generator antenna. \sys executed the
benchmark successfully without (NC) and with coalescing (WEG). The application
took longer to complete than at a shorter distance of 15\,cm in the previous
experiment, because of smaller (negligible) incoming energy at the larger
distance. The variant without coalescing (NC) slowed down by 2.16$\times$ and the
variant with WEG coalescing slowed down by 2.31$\times$ slower, but at both
distances, WEG completed faster than NC.
%
For comparison, the run time with Alpaca is effectively infinite at this
distance, which is a consequence of its non-adaptive static tasks.

>>>>

\textcolor{red}{In a separate experiment, we have enabled task downsizing in \sys and measured
the execution time for \textit{fft} benchmark at 60\,cm from the signal
generator antenna. \sys executed the
benchmark successfully without (NC) and with coalescing (WEG). The application
took longer to complete than at a shorter distance of 15\,cm in the previous
experiment, because of smaller (negligible) incoming energy at the larger
distance. The variant without coalescing (NC) slowed down by 2.16$\times$ and the
variant with WEG coalescing slowed down by 2.31$\times$ slower, but at both
distances, WEG completed faster than NC.}
%
For comparison, the run time with Alpaca is effectively infinite at this
distance, which is a consequence of its non-adaptive static tasks.
